%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[margin, 10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above

\setlength{\textwidth}{5.1in} % Text width of the document

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------

\moveleft.5\hoffset\centerline{\large\bf Joshua Taylor Eppinette} % Your name at the top
 
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'
 
\moveleft.5\hoffset\centerline{45 Lansing St Apt 2612} % Your address
\moveleft.5\hoffset\centerline{San Francisco, San Francisco 94105}
\moveleft.5\hoffset\centerline{(770) 401-6678}
\moveleft.5\hoffset\centerline{josheppinette@icloud.com}

%----------------------------------------------------------------------------------------

\begin{resume}

%----------------------------------------------------------------------------------------
%	OBJECTIVE SECTION
%----------------------------------------------------------------------------------------
 
\section{OBJECTIVE}  

To obtain a career that will allow myself to take full advantage of my passion and experience in software engineering, security and development operations. 

%----------------------------------------------------------------------------------------
%	Technology SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{TECHNOLOGY \\ SKILLS} 

{\sl Programming Languages:} Golang, Python, JavaScript. \\
{\sl Operations Technologies:} DO/AWS/GCE/Vultr Cloud Services, Docker, Terraform, Jenkins, Ansible, Vagrant. \\
{\sl Web Backend Technologies:} ModSecurity, Nginx, Consul, Vault, NodeJS, Django, MongoDB, PostgreSQL, Unbound, MailChimp, Minio. \\
{\sl Web Frontend Technologies:} VueJS, AngularJS, Leaflet, Selenium, Bootstrap, SASS, Gulp, Webpack, Bower, NodeJS. \\
 
%----------------------------------------------------------------------------------------
%	PROFESSIONAL EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
 
\section{EXPERIENCE}

{\sl Software Engineer} \hfill October 2017 - Present \\
Apple Inc, Cupertino, CA
\begin{itemize}
\item Tech lead in Global Network Compute Security group.
\item Integrated software engineering standards into group daily practices.
\item Leveraged Ansible to assist in the maintanence of a global fleet of web application firewalls and load balancers.
\item Developed and maintained services contributing to our internal and external security.
\item Analyzed and upgraded web application security standards for global WAF.
\end{itemize} 

{\sl Software Engineer} \hfill June 2015 - October 2017 \\
Ionic Security Inc, Atlanta, GA
\begin{itemize}
\item Developed and designed a large AngularJS web application.
\item Implemented and maintained multiple enterprise API authentication strategies in Golang and AngularJS.
\item Leveraged Golang's compiled nature to simplify deployments and decrease ops issues.
\item Developed and maintained the development environment used by front end software engineers.
\item Developed a distributed authentication and routing system for a SOA using Golang, Nginx, and Lua.
\item Integrated the Jenkins Continuous Integration(CI) systems into the existing deployment processes.
\item Implemented web application security standards defined by OWASP.
\end{itemize} 

{\sl Software Engineer} \hfill August 2013 - June 2015 \\
Georgia Tech Research Institute, Electronic Systems Laboratory, Atlanta, GA 
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Designed and developed Django/AngularJS software systems for the Department of Defense, Army, and Navy.
\item Presented software demos to Department of Defense derived clients.
\end{itemize}
 
{\sl Consultant, Owner} \hfill May 2014 - Present\\
JTE Technologies, Atlanta, GA
\begin{itemize} 
\item Designed and developed large Django/AngularJS and Golang/AngularJS software systems.
\item Setup continuous deployments for multiple projects of varying technologies through GitLab CI and Docker Swarm.
\item Provisioned and maintained multiple Docker Swarm clusters using Ansible and Terraform.
\end{itemize} 


%----------------------------------------------------------------------------------------
%	COMMUNITY SERVICE SECTION
%---------------------------------------------------------------------------------------- 

\section{COMMUNITY \\ SERVICE}

Kennesaw Mountain Trail Club, {\sl Volunteer} \hfill February 2014 - Present \\
Race Against Violence, {\sl Volunteer} \hfill October 2012 - Present \\
9\/11 Memorial Stair Climb For The Fallen Heroes, {\sl Volunteer \& Climber} \hfill September 2016 - Present \\

%----------------------------------------------------------------------------------------
%	EXTRA-CURRICULAR ACTIVITIES SECTION
%----------------------------------------------------------------------------------------

\section{EXTRA-CURRICULAR \\ ACTIVITIES} 

Kappa Sigma Fraternity, {\sl President} \hfill August 2014 - May 2015\\
Kappa Sigma Fraternity, {\sl Treasurer} \hfill December 2013 - August 2014 \\
Technology Student Association, {\sl Team Leader} \hfill August 2011 - May 2012 \\
 

%----------------------------------------------------------------------------------------

\end{resume}
\end{document}